\documentclass[a4paper]{tufte-handout}

\usepackage{dashrule}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{xfrac}
\usepackage{units}
\usepackage{draftwatermark}

\SetWatermarkText{Draft}
\SetWatermarkScale{1.5}

\title{Imperial College Dramatic Society Terms and Conditions of Hire}
% \author[The ICDS Committee]{The ICDS Committee}
\date{Initial draft, presented to Committee 27/10/15}

\newcommand{\policyOffset}{12pt}

\newcommand{\policyCspp}[2][\policyOffset]{\marginnote[#1]{\textsc{CSP Policy \S#2}}}
\newcommand{\policyCspEquip}[2][\policyOffset]{\marginnote[#1]{\textsc{CSP Equipment Policy \S#2}}}
\newcommand{\policyBye}[2][\policyOffset]{\marginnote[#1]{\textsc{Bye-laws \S#2}}}
\newcommand{\policyAE}[2][\policyOffset]{\marginnote[#1]{\textsc{A\&E Standing Orders \S#2}}}
\newcommand{\policyHs}[2][\policyOffset]{\marginnote[#1]{\textsc{Health \& Safety Policy \S#2}}}
\newcommand{\policyPub}[2][\policyOffset]{\marginnote[#1]{\textsc{Publicity Policy \S#2}}}
\newcommand{\policyTankard}[1][\policyOffset]{\marginnote[#1]{\textsc{Tankards Policy}}}

\addtolength{\hoffset}{24pt}

\begin{document}

\maketitle

\begin{fullwidth}
\itshape

\begin{abstract}

\end{abstract}
\end{fullwidth}

\hdashrule{15cm}{1.1pt}{1.1pt}

\section{Introduction}
\begin{enumerate}
    \item This document shall inherit all provisions and definitions given in the Imperial College Dramatic Society Constitution (ICDS Constitution).
    \item If this document conflicts with the ICDS Constitution, the ICDS Constitution shall take precedence.
    \item The Agreement shall refer to a specific instance of an ICDS Official Hire Agreement including the ICDS Official Quotation attached to the ICDS Official Hire Agreement.
    \item The Equipment shall refer to the equipment listed in the Agreement.
    \item The Hirer shall refer to that person, organisation, sub-committee of the Union, or a Club, Society or Project of the Union indicated as The Hirer on the Agreement.
    \item The Start Date shall refer to the start date indicated on the Agreement.
    \item The End Date shall refer to the end date indicated on the Agreement.
    \item The Period is the period of time from the Start Date until the End Date (inclusive).
    \item The Charge is the net payable total plus VAT at the indicated rate shown on the Agreement.
\end{enumerate}

\section{Provisions applying to ICDS}
\begin{enumerate}[resume]
    \item ICDS shall provide to the Hirer the Equipment on the Start Date, or any date prior to this as agreed with the Hirer.
    \item ICDS reserves the right to swap any item of the Equipment for an item which can fulfil the same role as the item specified on the Agreement.
    \item ICDS reserves the right to charge a fee in addition to the Charge in the event that the Equipment is returned to ICDS in an untimely, unsuitable or unsatisfactory manner.
    \item ICDS is fully and wholly indemnified against any financial liabilities which may arise as a result of an accident involving the Equipment.
    \item ICDS shall not be held liable for any loss of profits, business, revenue, goodwill, or savings by the Hirer, nor for any other special, indirect, or consequential loss of the Hirer.
    \item ICDS does not accept responsibility for failure or delay to its obligations under these Terms and Conditions due to circumstances beyond its control.
\end{enumerate}

\section{Provisions applying to the Hirer}
\begin{enumerate}[resume]
    \item The Hirer shall return the Equipment to ICDS on the End Date, or any date prior to this as agreed with ICDS.
    \item The Hirer is responsible for arranging suitable transportation to and from the Ground Floor or Level 1 of the Imperial College Union building on the north side of Beit Quad.
    \item The Hirer shall ensure that the Equipment is used by competent personnel in a manner which complies with all applicable Union and Government regulations and statutes, including but not limited to the Health and Safety at Work etc Act 1974.
    \item The Hirer shall return the Equipment in the same condition that they obtained it. Failure to do so shall constitute returning the Equipment in an unsuitable manner as per \S12.
    \item The Hirer shall return to ICDS all Equipment, including any items considered faulty or non-functional by the Hirer (such as lamps and light bulbs), by the End Date. Failure to do so shall constitute returning the Equipment in an unsuitable manner as per \S12.
    \item The Hirer shall ensure that the Equipment is insured at the value indicated on the Agreement.
    \item The Hirer shall have no rights to the Equipment other than as indicated in this document.
    \item The Hirer shall not sub-let or further give control of the Equipment to any other person, organisation, sub-committee of the Union, or Club, Society or Project of the Union.
    \item The Hirer must pay on demand the Charge plus any additional fees as defined in \S12.
    \item In the event of loss or damage to the Equipment during the Period the Hirer is liable in full to the costs of replacement or restoration to good working order of the Equipment.
\end{enumerate}

\section{General Provisions}
\begin{enumerate}[resume]
    \item The Equipment shall at all times remain the property of Imperial College Union under the care of ICDS.
    \item If the Charge exceeds \pounds20 and the Hirer is a Club, Society, or Project of the Union, a financially responsible member of the Executive Committee of the Hirer's Management Group must additionally indicate that they are confident that the Hirer will be able to pay the Charge on demand.
    \item Further, if the Charge exceeds \pounds1000 and the Hirer is a Club, Society or Project of the Union, a Deputy President of the Union must indicate that the Union is willing to guarantee payment of Charge to ICDS in the event that the Hirer fails to pay.
    \item No neglect, delay, or indulgence of ICDS in the enforcing of these Terms and Conditions shall prejudice the rights of ICDS under these Terms and Conditions.
\end{enumerate}

\end{document}